\chapter{Results}

The development of our gateway resulted in some small demos for the endpoints
we developed over time and one final comprehensive demo that used many of the
developed features in one unified story. The scenario for the demo was a truck
fleet management system and an infotainment system within the trucks. There
were two trucks in the region of a port, one in standby in the waiting area and
another approaching said waiting area.

The first truck is shown to be creating an account in the infotainment system
where we demonstrate a real life case of the use of the OTP SMS API since a
phone number is necessary to validate the account. Following this we show the
driver watching a video with good quality on the infotainment system.

Moving to the fleet managers view, we can see him looking at a dashboard where
he can associate trucks and their phone numbers with their current state, that
is wether they are or aren't in the queue region and wether they are or aren't
reachable by the network.

Initially the second truck is not reachable by network since the network
conenctivity only appears closer to the port itself, but as soon as the truck
becomes reachable the fleet manager is notified. This is an example of a
situation where the Device Reachability Subscription API is used. Following
this the fleet manager then moves to a view of the details of the truck that is
approaching the port. Here he can see the current position of the truck along
with a dashcam that is streaming with low quality. Once again here we show a
use case for the Location Retrieval API with the realtime position of the
truck.

Following this the truck enters the waiting area for the port, at which point
the fleet manager receives a notification and an increase in bandwidth for the
dashcam is made with a noticeable increase in quality, this happens at the same
time as the first truck receives a decrease in bandwidth, which results in a
big reduction in quality for the video on the infotainment system. This shows
how two of the developed APIs can be used together to give priority to a more
critical device, in this case the moving truck. Here we utilize the Geofencing
Subscription API to issue the notification and to change the bandwidth on both
trucks, which is done using a different API, in this case the QoD Provisioning
API.

\section{Implementation}
